Estimating individual subjective values of emotion regulation strategies

### 2022-02-22 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
added NFC description

>>>>

*Implicit theories of willpower.*

*Need for Cognition.*
Need for Cognition (NFC) was assessed with the 16-item short version of the German NFC scale [@Bless1994]. 
Responses to each item (e.g., "Thinking is not my idea of fun", recoded) were recorded on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree) and were summed to the total NFC score. 
The scale shows comparably high internal consistency [Cronbach’s $\alpha>.80$; @Bless1994; @Fleischhauer2010] and a retest reliability of $r_{tt}=.83$ across 8 to 18 weeks [@Fleischhauer2015].
